Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-08-30 paper/paper.tex
Added a graph Craig wanted.

\end{proof}
\begin{figure}
    \begin{center}
        \begin{tikzpicture}{every node/.style={circle, inner sep=1mm}}
            \node[fill=black] (p)  {};
            \node[fill=red] (n1) [above left of = p] {};
            \node[fill=blue] (n2) [above of = p] {};
            \node[fill=blue] (n3) [above right of = p] {};
            \node[fill=green] (q) [above of = n2] {};
            %\path[]
        \end{tikzpicture}
        \caption{Graph that Craig wanted}
        \label{fig:nds}
    \end{center}
\end{figure}

>>>>

\end{proof}
\begin{figure}
    \begin{center}
        \begin{tikzpicture}[every node/.style={circle, inner sep=1mm}]
            \node[fill=black] (p) {};
            \node[draw=none,right of = p,node distance=3mm,yshift=-1mm] {$p$};
            \node[fill=uofglawn] (n2) [above of = p,node distance=12mm] {};
            \node[fill=uofgpumpkin] (n1) [left of = n2] {};
            \node[fill=uofglawn] (n3) [right of = n2] {};
            \node[fill=uofgcobalt] (q) [above of = n2,node distance=12mm] {};
            \path (p) edge (n1) edge (n2) edge (n3)
                (n1) edge (q)
                (n2) edge (n3) edge (q)
                (n3) edge (q);
        \end{tikzpicture}
        \caption{Graph that Craig wanted}
        \label{fig:nds}
    \end{center}
\end{figure}
